### 2014-10-31 TransitionsUsefulFirst.tex
stuff

%\begin{figure}
%\small
%\centering
%\begin{boxedminipage}[c]{.48\textwidth}
%%\centering
%\inference
%[Halt]
%{\theta(i) = (s, \pc) & \dec(s,\pc) = H}
%{\io{SC}{\theta,m}{H}{}}
%
%\inference
%[NonMem]
%{\theta(i) = (s, \pc) & \dec(s,\pc) = (\nm, x) \\ \exec(s, \pc, (\nm, x)) = (\pc', s')}
%{\io{SC}{\theta,m}{\theta[i \coloneqq (s', \pc')], m}{}}
%
%\inference
%[Load]
%{\theta(i) = (s,\pc) & \dec(s,\pc) = (\ld, x, a) \\ \exec(s, \pc, (\ld, x, m(a))) = (\pc', s')}
%{\io{SC}{\theta,m}{\theta[i\coloneqq(s',\pc')],m}{}}
%
%\inference
%[Store]
%{\theta(i) = (s,\pc) & \dec(s,\pc) = (\st, a, v) \\ \exec(s, \pc, (\st)) = (\pc', s')}
%{\io{SC}{\theta,m}{\theta[i\coloneqq(s',\pc')],m[a\coloneqq v]}{}}
%\end{boxedminipage}
%\caption{LTS for sequential consistency with $n$ simple processors}
%\label{Ref}
%\end{figure}
%
\section{Decomposing a Multi-Processor System}
\label{sec:store-atomicity}

>>>>

%\begin{figure}
%\small
%\centering
%\begin{boxedminipage}[c]{.48\textwidth}
%%\centering
%\inference
%[Halt]
%{\theta(i) = (s, \pc) & \dec(s,\pc) = H}
%{\io{SC}{\theta,m}{H}{}}
%
%\inference
%[NonMem]
%{\theta(i) = (s, \pc) & \dec(s,\pc) = (\nm, x) \\ \exec(s, \pc, (\nm, x)) = (\pc', s')}
%{\io{SC}{\theta,m}{\theta[i \coloneqq (s', \pc')], m}{}}
%
%\inference
%[Load]
%{\theta(i) = (s,\pc) & \dec(s,\pc) = (\ld, x, a) \\ \exec(s, \pc, (\ld, x, m(a))) = (\pc', s')}
%{\io{SC}{\theta,m}{\theta[i\coloneqq(s',\pc')],m}{}}
%
%\inference
%[Store]
%{\theta(i) = (s,\pc) & \dec(s,\pc) = (\st, a, v) \\ \exec(s, \pc, (\st)) = (\pc', s')}
%{\io{SC}{\theta,m}{\theta[i\coloneqq(s',\pc')],m[a\coloneqq v]}{}}
%\end{boxedminipage}
%\caption{LTS for sequential consistency with $n$ simple processors}
%\label{Ref}
%\end{figure}
%
It is worth noting that the LTS notation described above, along with the
composition operators are very similar to the semantics of hardware designs
written in Bluespec. As an example consider an inference rule in LTS and the
corresponding code in Bluespec in Figure \ref{both}. This code was actually
written for the PowerPC system \cite{Khan:PowerPc} (we will be using this rule
later in the paper when we describe the coherent caches).

\begin{figure*}
\centering
\begin{boxedminipage}{.53\textwidth}
\noindent \textbf{rule} $(c.\parent == p \; \mathit{\&\&} \; c.\s[a] < x \; \mathit{\&\&} \; c.\wt[a]==None);$

\hspace{1cm} $\ch[c][p][\req].\enq(a,c.\s[a],x); c.\wt[a] \Leftarrow x;$

\textbf{endrule}
\end{boxedminipage}
\begin{boxedminipage}{\textwidth}
\inference[]
{\parent(c,p) & \s(c,a) < x & \wt(c,a) = \epsilon}
{\ioxe{$M_c$}
{\dt, \ch, \s, \dst, \wt, \dwt, \inp, \outp}
{\dt, \ch[ (c, p, \req) \coloneqq
(a, \s(c, a), x) \uplus \ch(c,p,\req)], \s, \dst,\\
\wt[(c,a)\coloneqq x], \dwt, \inp, \outp}}
\end{boxedminipage}
\caption{Rule in Bluespec and its corresponding LTS transliteration}
\label{both}
\end{figure*}

\section{Decomposing a Multi-Processor System}
\label{sec:store-atomicity}
